Unity in diversity: Children from 17 diverse communities process gaze in similar ways

### 2024-03-19 supplement/supplement.Rmd
clean repo

---
title: "Unity in diversity: Children from 17 diverse communities process gaze in similar ways"
subtitle: "Supplemental material"
author: "..."
output: 
  bookdown::pdf_document2:
    toc: yes 
    number_sections: false    
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    #code_folding: hide
    number_sections: false
bibliography: library.bib
#csl: pnas.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\figurename}{Supplementary Figure}
  \renewcommand{\tablename}{Supplementary Table}
---

>>>>

---
title: "Unity in diversity: Children from 17 diverse communities process gaze in similar ways"
subtitle: "Supplemental material"
author: "..."
output: 
  bookdown::pdf_document2:
    toc: yes 
    number_sections: false    
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    #code_folding: hide
    number_sections: false
bibliography: ../paper/library.bib
csl: science.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\figurename}{Supplementary Figure}
  \renewcommand{\tablename}{Supplementary Table}
---
